---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

# Swiss Municipality Data Merger Tool

## Introduction

R Package which helps merge municipal level data sets available for different points in time.

In Switzerland, the landscape of municipalities is changing rapidly mainly due to mergers. 

* Number of municipalities in 2000: 2'899
* Number of municipalities in 2021: 2'163

The Swiss Municipal Data Merger Tool automatically detects these mutations and maps municipalities over time, i.e. municipalities of an old state to municipalities of a new state. This functionality is helpful when working with datasets that are based on different spatial references like for example Swiss voting data.

## Installation

```{r, eval = FALSE}
# Install released version from CRAN
install.packages("SMMT")
```

## Get started

* Read the vignette  `vignette("manual")`
* Look up the documentation of `?map_old_to_new_state`

## Resources

* Obtain the latest offical release from [CRAN](https://cran.r-project.org/package=SMMT)
* For more details, see [this article](https://onlinelibrary.wiley.com/doi/full/10.1111/spsr.12487) in the Swiss Political Science Review.
